Trends of SDR in Thessaloniki

### 2023-05-16 Article.Rmd
Commit 2023-05-16 13:17

---
title:         "Trends of downward SDR in Thessaloniki"
author:
  - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
  - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
abstract:
  "Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions."

@@

@@

>>>>

---
title:         "Trends of SDR in Thessaloniki"
author:
  - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
  - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
abstract:
  "Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions."

@@

<!-- SDR or GHI -->

@@

The shortwave downward solar irradiance (SDR) at the Earth's surface plays s significant role, on the climate.
Changes of the SDR can be related to major changes on the factors affecting the radiative forcing balance.
In this study we examine the trends of SDR with the ground-based measurements at Thessaloniki for the period 1993 - 2023.

[@Bais2013]
